SDR enhancement by clouds

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 14:14

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid)
- days without clouds and EC events
- days with    clouds and EC events
- random days
- manual selected days

@@

Sky Camera for some cases

Objectivity

Describe set of reference days we used to evaluate

Example of days plot?

>>>>

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid)
- any day without clouds and EC events
- 20 days with at least 60% of day length without clouds and some EC events
- 30 random days
- some manual selected days that were included during the manual inspection

For some of this edge cases we further use images from a skycam, in order to evaluate our selection of the thresholds.

@@

Include Example of days plot?
